Road Segment Prioritization for Bicycle Infrastructure

### 2020-11-06 README.Rmd
update growth figures

---
title: Road Segment Prioritization for Bicycle Infrastructure
date: "`r Sys.Date()`"
geometry: margin=2cm
bibliography: mybibfile.bib
#linenumbers: true
numbersections: true
#output: rticles::elsevier_article
output:
  # bookdown::github_document2
  bookdown::pdf_document2:
    extra_dependencies: ["subcaption", "longtable"]
---

>>>>

---
title: Road Segment Prioritization for Bicycle Infrastructure
date: "`r Sys.Date()`"
geometry: margin=2cm
bibliography: mybibfile.bib
#linenumbers: true
numbersections: true
#output: rticles::elsevier_article
output:
  bookdown::github_document2
  # bookdown::pdf_document2:
  #   extra_dependencies: ["subcaption", "longtable"]
---
